---
title: "Conmebol Visualizations"
author: "Luis Noguera & Nicolas Kaswalder"
date: "7/18/2020"
output: html_document
---


# Data Load

```{r}
source("Data Cleaning Script.R")

Conmebol %>% 
   kable() %>%
  kable_styling(c("striped", "bordered"))
  
```


# Data Exploration

# Histograms

```{r}
plot_histogram(Conmebol, geom_histogram_args = list(bins = 30L), ggtheme = theme_classic())

Conmebol %>% 
  ggplot(aes(x = skill, color=position)) +
  ggtitle("Skill by Position") +
  theme(plot.title = element_text(hjust = 0.5))+
  geom_histogram() +
  geom_vline(aes(xintercept=mean(skill)),
            color="dark blue", linetype="dashed", size=1)+
  scale_x_continuous(labels = comma)

Conmebol %>% 
  ggplot(aes(x = overall, color=position)) +
  geom_histogram() +
  ggtitle("Overall by Position") +
  theme(plot.title = element_text(hjust = 0.5))+
  geom_vline(aes(xintercept=mean(overall)),
            color="dark blue", linetype="dashed", size=1)+
  scale_x_continuous(labels = comma)


Conmebol %>% 
  ggplot(aes(x = total_goalkeeping, color=position)) +
  geom_histogram() +
    ggtitle("Goalkeeping skills by Position") +
  theme(plot.title = element_text(hjust = 0.5))+
  geom_vline(aes(xintercept=mean(total_goalkeeping)),
            color="dark blue", linetype="dashed", size=1)+
  scale_x_continuous(labels = comma)

Conmebol %>% 
  ggplot(aes(x = dribbling, color=position)) +
    ggtitle("Dribbling skills by Position") +
  theme(plot.title = element_text(hjust = 0.5))+
  geom_histogram() +
  geom_vline(aes(xintercept=mean(dribbling)),
            color="dark blue", linetype="dashed", size=1)+
  scale_x_continuous(labels = comma)

Conmebol %>% 
  ggplot(aes(x = finishing, color=position)) +
  ggtitle("Finishing skills by Position") +
  theme(plot.title = element_text(hjust = 0.5))+
  geom_histogram() +
  geom_vline(aes(xintercept=mean(finishing)),
            color="dark blue", linetype="dashed", size=1)+
  scale_x_continuous(labels = comma)

Conmebol %>% 
  select(skill, overall, total_goalkeeping, dribbling, finishing) %>% 
  summary()
```

# Histograms by Position
```{r}

#Lets look at our Goalkeepers

Conmebol %>% 
  filter(position == 'GK') %>% 
  ggplot(aes(x = total_goalkeeping, color=foot)) +
  ggtitle("Goalkeeing skills for Goalkeepers") +
  theme(plot.title = element_text(hjust = 0.5))+
  geom_histogram() +
  geom_vline(aes(xintercept=mean(total_goalkeeping)),
            color="dark blue", linetype="dashed", size=1)+
  scale_x_continuous(labels = comma)

#Lets look at our Defense

Conmebol %>% 
  filter(position == 'DEF') %>% 
  ggplot(aes(x = defense, color=best_position)) +
  ggtitle("Defense skills for Defensive Players") +
  theme(plot.title = element_text(hjust = 0.5))+
  geom_histogram() +
  geom_vline(aes(xintercept=mean(defense)),
            color="dark blue", linetype="dashed", size=1)+
  scale_x_continuous(labels = comma)

#Lets look at our Midfildiers

#First lets see their control
Conmebol %>% 
  filter(position == 'MID') %>% 
  ggplot(aes(x = control, color=best_position)) +
  ggtitle("Short Passing skills for Midfilders") +
  theme(plot.title = element_text(hjust = 0.5))+
  geom_histogram() +
  geom_vline(aes(xintercept=mean(control)),
            color="dark blue", linetype="dashed", size=1)+
  scale_x_continuous(labels = comma)

#Lets look at their dribbling

Conmebol %>% 
  filter(position == 'MID') %>% 
  ggplot(aes(x = dribbling, color=best_position)) +
  ggtitle("Dribbling skills for Midfilders") +
  theme(plot.title = element_text(hjust = 0.5))+
  geom_histogram() +
  geom_vline(aes(xintercept=mean(dribbling)),
            color="dark blue", linetype="dashed", size=1)+
  scale_x_continuous(labels = comma)

#Lets finally look at their short_passing

Conmebol %>% 
  filter(position == 'MID') %>% 
  ggplot(aes(x = short_passing, color=best_position)) +
  ggtitle("Short Passing skills for Midfilders") +
  theme(plot.title = element_text(hjust = 0.5))+
  geom_histogram() +
  geom_vline(aes(xintercept=mean(short_passing)),
            color="dark blue", linetype="dashed", size=1)+
  scale_x_continuous(labels = comma)

#Lets look at our Strikers

#Lets look at their attacking skills

Conmebol %>% 
  filter(position == 'ATT') %>% 
  ggplot(aes(x = attacking, color=best_position)) +
  ggtitle("Attacking skills for Strikers") +
  theme(plot.title = element_text(hjust = 0.5))+
  geom_histogram() +
  geom_vline(aes(xintercept=mean(attacking)),
            color="dark blue", linetype="dashed", size=1)+
  scale_x_continuous(labels = comma)

#Lets look at their finishing

Conmebol %>% 
  filter(position == 'ATT') %>% 
  ggplot(aes(x = finishing, color=best_position)) +
  ggtitle("Finishing skills for Strikers") +
  theme(plot.title = element_text(hjust = 0.5))+
  geom_histogram() +
  geom_vline(aes(xintercept=mean(finishing)),
            color="dark blue", linetype="dashed", size=1)+
  scale_x_continuous(labels = comma)

```

## Basic Histogram of Player's Value and Position

```{r}

#Lets look at our value for all players
Conmebol %>% 
  ggplot(aes(x = value, color=position)) +
  ggtitle("Value per Position") +
  theme(plot.title = element_text(hjust = 0.5))+
  geom_histogram() +
  geom_vline(aes(xintercept=mean(position)),
            color="dark blue", linetype="dashed", size=1)+
  scale_x_continuous(labels = comma)


#Lets look at the players whose value are greater than 10Million
Conmebol %>% 
    filter(value >= 10000000) %>% 
  ggplot(aes(x = value, color=position)) +
  ggtitle("Value per Position") +
  theme(plot.title = element_text(hjust = 0.5))+
  geom_histogram() +
  geom_vline(aes(xintercept=mean(position)),
            color="dark blue", linetype="dashed", size=1)+
  scale_x_continuous(labels = comma)

#Lets look at the players whose value are less than 500k

Conmebol %>% 
    filter(value <= 500000) %>% 
  ggplot(aes(x = value, color=position)) +
  ggtitle("Value per Position") +
  theme(plot.title = element_text(hjust = 0.5))+
  geom_histogram() +
  geom_vline(aes(xintercept=mean(position)),
            color="dark blue", linetype="dashed", size=1)+
  scale_x_continuous(labels = comma)


Conmebol %>% 
  select(value) %>% 
  summary()

```

*Insights*

- Biggest portion of the players are under $EU 30,000,000$
- A very small number of players above $EU 60,000,000$ and 2 players above $EU 90,000,000$
- Median of $EU 3,400,000$

```{r}

# Overall rating by position
Conmebol %>%
  mutate(best_position = fct_reorder(best_position, overall, .fun = median)) %>%
  ggplot(aes(best_position, overall)) +
  geom_boxplot() +
  coord_flip()+
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(
    panel.border = element_blank(),
    panel.background = element_rect(colour = "black"),
plot.title = element_text(color="dark green", size=14, face="bold.italic"),
axis.title.x = element_text(color="dark blue", size=14, face="bold"),
axis.title.y = element_text(color="dark red", size=14, face="bold"))+
  labs(x = "Overall", y = "Best Position", title = 'Overall Rating by Position')

# Overall by foot for strikers in the dataset

Conmebol %>%
  filter(best_position%in% c('ST', 'RW', 'LW', 'CF')) %>%
  mutate(foot = fct_reorder(foot, overall)) %>%
  ggplot(aes(foot, overall, fill = foot)) +
  geom_boxplot() +
  facet_wrap(~best_position, scales = 'free') +
  theme(
plot.title = element_text(color="dark green", size=14, face="bold.italic"),
axis.title.x = element_text(color="blue", size=14, face="bold"),
axis.title.y = element_text(color="dark red", size=14, face="bold"))+
  labs(x = 'Foot', y = 'Overall') +
  scale_fill_discrete(name="Foot")



```

# South America Map Visualization

```{r}


## Average per Country Map
Overall_avg_LATAM <- ggplot(Conmebol, aes(reorder(nationality, -overall), overall))  +
  geom_text(aes(label = round(overall,2)), hjust = -0.05) +
  geom_bar(stat = 'identity')  +
  labs(y= 'Overall Average',
       x= "Country") +
  theme_light() +
  coord_flip()
Overall_avg_LATAM


# World Map

## Loading Map data
worldmap <- map_data('world')

merged_data2 <- Conmebol_numerical %>% 
  inner_join(worldmap, by = c('nationality' = 'region')) %>%
  group_by(nationality) %>%
  summarise(Overall_Median = median(overall)) %>%
  ungroup() %>%
  inner_join(worldmap, by = c('nationality' = 'region')) %>%
  select(Overall_Median, lat, long, nationality, group)

overall_map <- ggplot(data = merged_data2, aes(x = long, y = lat, group = group)) +
  geom_polygon(aes(fill = Overall_Median)) +
  labs(fill='Total Player Counts')


## Interactive Plot
ggplotly(overall_map)


```

# Scatter Plot 

## Market Value and Overall overall of the Players by Nationality

```{r}

Conmebol %>% 
  filter(value != 0.0) %>%
  mutate(nationality = fct_lump_min(nationality, 60)) %>%
  ggplot(aes(value, overall)) +
  geom_point() +
  geom_smooth(method = 'gam') +
  facet_wrap(~nationality, scales = 'free') +
  scale_x_continuous(labels = scales::dollar_format())


```


# Correlation among Numerical Variables


```{r}

conmebol_num <- Conmebol %>% 
  select(-id, -height, -name, -best_position, -foot, -nationality) %>%
  mutate(cost = case_when(value > 10000000 ~ "High",
                                                 TRUE ~ 'Low'),
                          value = log(value))
  

library(GGally)
# Highly correlated dataset - Will try regularization method Lasso or Ridge and a Random Forest model. 
ggscatmat(conmebol_num, columns = 1:6, color = "cost", alpha =  0.7)

```

